### 2013-05-16 inst/examples/BUGS/allen.Rmd
replicate run. cache results

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA,
               fig.width=6, fig.height=4)

@@

##

```{r step_ahead}
gp_f_at_obs <- gp_predict(gp, x, burnin=1e4, thin=300)

step_ahead <- function(x, f, p){
  h = 0
  x_predict <- sapply(x, f, h, p)
  n <- length(x_predict) - 1
  y <- c(x[1], x_predict[1:n])
  y
}

df <- melt(data.frame(time = 1:length(x), stock = x, 
                GP = gp_f_at_obs$E_Ef,
                True = step_ahead(x,f,p),  
                MLE = step_ahead(x,f,est$p), 
                Parametric.Bayes = step_ahead(x, f, bayes_pars), 
                Ricker = step_ahead(x,alt$f, ricker_bayes_pars), 
                Myers = step_ahead(x, Myer_harvest, myers_bayes_pars)
                 ), id=c("time", "stock"))

ggplot(df) + geom_point(aes(time, stock)) + 
  geom_line(aes(time, value, col=variable)) +
    scale_colour_manual(values=colorkey) 
```

@@

```{r}
OPT = data.frame(opt_gp$D, opt_true$D, opt_estimated$D, opt_alt$D, opt_par_bayes$D, myers_alt$D)

names(OPT) = names(colorkey)[1:6]
```

>>>>

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE, comment=NA,
               fig.width=6, fig.height=4, cache.path="allencache/")

@@

@@

```{r}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_alt$D, Parametric.Bayes = opt_par_bayes$D, Myers = myers_alt$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```
